### 2016-06-29 publications/Journal/3-features.tex
Added references

We primarily investigate this for optimistic simulation, as this is the most memory consuming mode of simulation~\cite{Fujimoto}.
Simulation execution times for all four combinations are shown in Figure~\ref{fig:memallocators_parallel}.
Optimistic simulation greatly benefits from the use of \textit{tcmalloc}, regardless of the allocator.
Nonetheless the pool allocator also reduces the allocation overhead, though only by a relatively small fraction.
Both techniques are required to reduce the overhead of memory allocations in dxex, and on by default.

@@

\subsubsection{Random Number Generators}
Random Number Generators (RNG) are another aspect of the program that results in sequentialization.
All accesses to the RNG will result in the modification of a global (\textit{i.e.}, shared between threads) variable.
This easily becomes a bottleneck in simulation, since random numbers are a common occurence in simulation~\cite{?}.
As such, a non-trivial amount of time in a simulation is often spent waiting for an RNG.

@@

We see in Figure~\ref{fig:Queuerngspeedup} that storing the RNG in the state is very expensive for the default STL random number generator.
%TODO fill in values
This is primarily caused by the significant difference in size: 2504 bytes for the STL random number generator, and 24 bytes for the Tina random number generator.
Dxex's sequential and conservative kernels are insensitive to storing the RNG object in the atomic model state, since no copying/state saving occurs in dxex conservative simulation.
The optimistic kernel is clearly affected, as it needs to copy more bytes in every transition due to state saving.

>>>>

We primarily investigate this for optimistic simulation, as this is the most memory consuming mode of simulation~\cite{FujimotoBook}.
Simulation execution times for all four combinations are shown in Figure~\ref{fig:memallocators_parallel}.
Optimistic simulation greatly benefits from the use of \textit{tcmalloc}, regardless of the allocator.
Nonetheless the pool allocator also reduces the allocation overhead, though only by a relatively small fraction.
Both techniques are required to reduce the overhead of memory allocations in dxex, and on by default.

@@

\subsubsection{Random Number Generators}
Random Number Generators (RNG) are another aspect of the program that results in sequentialization.
All accesses to the RNG will result in the modification of a global (\textit{i.e.}, shared between threads) variable.
This easily becomes a bottleneck in simulation, since random numbers are a common occurence in simulation~\cite{Random}.
As such, a non-trivial amount of time in a simulation is often spent waiting for an RNG.

@@

We see in Figure~\ref{fig:Queuerngspeedup} that storing the RNG in the state is very expensive for the default STL random number generator.
This is primarily caused by the significant difference in size: 2504 bytes for the STL random number generator, and 24 bytes for the Tina random number generator.
Dxex's sequential and conservative kernels are insensitive to storing the RNG object in the atomic model state, since no copying/state saving occurs in dxex conservative simulation.
The optimistic kernel is clearly affected, as it needs to copy more bytes in every transition due to state saving.

### 2016-06-29 publications/Journal/4a-allocation.tex
Added references

The PHOLDTree model is similar in structure to models of gossiping in social networks~\cite{?}, hierarchical resource sharing~\cite{?} or load balancing~\cite{?}.
The lookahead of an atomic node is the minimally allowed $\epsilon$, indicating uncertainty, as is often the case in realistic models.
We demonstrate the importance of allocation, by comparing a breadth-first versus a depth-first scheme.

>>>>

The PHOLDTree model is similar in structure to models of gossiping in social networks~\cite{Gossip} and multi-granularity locking~\cite{MultiGranularityLocking}.
The lookahead of an atomic node is the minimally allowed $\epsilon$, indicating uncertainty, as is often the case in realistic models.
We demonstrate the importance of allocation, by comparing a breadth-first versus a depth-first scheme.
